---
title: "exportingMACStoBED"
author: "Tommy"
date: "25 February 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r cars}
listOfPeaks <- GRangesList(lapply(macsPeaks,function(x)ChIPQC:::GetGRanges(x,sep="\t",simplify=T)))
flattenedPeaks <- reduce(unlist(listOfPeaks))
names(listOfPeaks) <- gsub("\\.xls","\\.bed",basename(macsPeaks))
lapply(1:length(listOfPeaks),function(x)export.bed(listOfPeaks[[x]],con=names(listOfPeaks)[x]))
flattenedPeaks <- reduce(unlist(listOfPeaks))
export.bed(flattenedPeaks,con="flattenedPeaks.bed")

matOfOverlaps <- sapply(listOfPeaks,function(x)
(flattenedPeaks %over% x)+0
)

colnames(matOfOverlaps) <- basename(gsub("_peaks\\.xls","",macsPeaks))


elementMetadata(flattenedPeaks) <- matOfOverlaps

mych12Peaks <- flattenedPeaks[elementMetadata(flattenedPeaks)$mycch12rep1 + elementMetadata(flattenedPeaks)$mycch12rep2 == 2]
mycMelPeaks <- flattenedPeaks[elementMetadata(flattenedPeaks)$mycmelrep1 +  elementMetadata(flattenedPeaks)$mycmelrep2 == 2]

export.bed(mycMelPeaks,con="Mel_HighCon_flattenedPeaks.bed")
export.bed(mych12Peaks,con="Ch12_HighCon_flattenedPeaks.bed")


mycMelPeaks_Only <- flattenedPeaks[elementMetadata(flattenedPeaks)$mycmelrep1 + elementMetadata(flattenedPeaks)$mycmelrep2 == 2 &
elementMetadata(flattenedPeaks)$mycch12rep1 + 
                 elementMetadata(flattenedPeaks)$mycch12rep2 == 0]

export.bed(mycMelPeaks_Only,con="Mel_Only_HighCon_flattenedPeaks.bed")


mycMelorch12Peaks <- flattenedPeaks[elementMetadata(flattenedPeaks)$mycmelrep1 + elementMetadata(flattenedPeaks)$mycmelrep2 == 2 |
elementMetadata(flattenedPeaks)$mycch12rep1 + 
                 elementMetadata(flattenedPeaks)$mycch12rep2 == 2]

export.bed(mycMelorch12Peaks,con="Mel_Or_Ch12_HighCon_flattenedPeaks.bed")

firstPeakSet <- ChIPQC:::GetGRanges(macsPeaks[1], sep="\t", simple=F)
secondPeakSet <- ChIPQC:::GetGRanges(macsPeaks[2], sep="\t", simple=F)

allPeaks <- c(firstPeakSet,secondPeakSet)
allPeaksReduced <- reduce(allPeaks)
length(allPeaks)
length(allPeaksReduced)

export.bed(allPeaksReduced,con="Ch12_flattenedPeaks.bed")

commonPeaks <- allPeaksReduced[allPeaksReduced %over% firstPeakSet & allPeaksReduced %over% secondPeakSet]
export.bed(commonPeaks,con="Ch12_common_flattenedPeaks.bed")


